Manuscript Body

### 2024-03-06 Markdown/Manuscript/Child_RMDs/MS_Body.Rmd
safety

## Author contributions
MPH led the conceptualisation and software implementation of ready4 and readyforwhatsnext and manuscript drafting. MH, CG and GW co-authored the software described in this article. All co-authors critically reviewed and revised manuscript drafts and approved the final manuscript text.

>>>>

## Author contributions{-#author-contributions}
MPH led the conceptualisation and software implementation of ready4 and readyforwhatsnext and manuscript drafting. MPH, CG and GW co-authored the software described in this article. All co-authors critically reviewed and revised manuscript drafts and approved the final manuscript text.
